\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{multicol}

% Various Document Settings
\leftmargin=0.15in
\oddsidemargin=0.15in
\textwidth=6.0in
\topmargin=-0.20in
\textheight=9.25in
\raggedright
\pagenumbering{arabic}
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

%% BEGIN DEFINITIONS %%

% New configurations for lists
\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}


\newcommand{\lineover}{
    \begin{changemargin}{-0.05in}{-0.05in}
        \vspace*{-8pt}
        \hrulefill \\
        \vspace*{-2pt}
    \end{changemargin}
}

% Header
\newcommand{\header}[1]{
    \begin{changemargin}{-0.5in}{-0.5in}
        \scshape{#1}\\
        \lineover
    \end{changemargin}
}

% Contact Display Format
\newcommand{\contact}[4]{
    \begin{changemargin}{-0.5in}{-0.5in}
        \begin{center}
            {\Large \scshape {#1}}\\ \smallskip
            {#2}\\ \smallskip
            {#3}\\ \smallskip
            {#4}\smallskip
        \end{center}
    \end{changemargin}
}

% Document Margins
\newenvironment{body} {
    \vspace*{-16pt}
    \begin{changemargin}{-0.20in}{-0.5in}
  }
    {\end{changemargin}
}

% School Display Format
%\newcommand{\school}[4]{
%    \textbf{#1} \hfill \emph{#2\\}
%    #3\\
%    #4\\
%}

%% BEGIN DOCUMENT %%

\begin{document}

% Contact Information
\contact{Sebastian Imlay}{sebastian.imlay@gmail.com}{208.290.4936}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Objective
%\header{Objective}

%\begin{body}
%\vspace{14pt}
%Seeking a position in academic leadership or professional industry opportunities that utilizes my communication, analytical thinking and problem-solving skills to encourage, nurture and guide student creativity and learning.
%\end{body}

%\smallskip

% Professional summary
%\header{Professional Summary}

%\begin{body}
%\vspace{14pt}
%Professional student double majoring in Math \& Computer Science, working as Vice President for Business \& Operations of university student government, and leading a small technical team in part-time internship. Has particular expertise in problem solving, critical thinking, organization, individual and group goal-setting, facilitating collaboration and communicating in/with small and large groups.
%\end{body}

%\smallskip

% Qualifications Summary
%\header{Qualifications Summary}
%
%\vspace{14pt}
%\begin{body}
%Motivated student with dual concentration in Mathematics \& Computer Science. Proven leadership capabilities serving as student representative in student
%government, and managing other student managers in non-profit organization. Strong background and technical skills related to area of study demonstrated by
%leading a team of interns in mobile application development, developing software extensions for corporate fraud management system, and teaching/tutoring
%students as a Teaching Assistant for introductory Computer Science courses.
%
%\end{body}

%\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Experience
\header{Experience}

\begin{body}
    \vspace{14pt}

    \textbf{Data Scientist/Software Engineer}, \emph{Vehicle Data Science Inc.} \hfill \emph{August 2013 - November 2013}\\
    \vspace*{-4pt}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Design and implementation of Computational Geometry Algorithms for GPS data
        \item Geospatial analysis of vehicle data.
        \item Database schema design and implementation.
        \item Worked with Python, Bash, Git, Numpy, SQLAlchemy, Postgres, PostGIS
    \end{itemize}

    \textbf{Software Engineer Intern}, \emph{Yelp, San Francisco, CA} \hfill \emph{Summer 2013}\\
    \vspace*{-4pt}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Worked with a team to import and export features to and from the Yelp database.
        \item Ran analysis on data using Python Streams and MapReduce.
        \item Received Hackathon “Most Useful Award”.
        \item Worked with Python, Bash, Make and Git.
    \end{itemize}

    \textbf{Software Engineer Intern}, \emph{Synapse Product Development, Seattle, WA} \hfill \emph{Winter 2013}\\
    \vspace*{-4pt}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Implemented recognition for accelerometer time series data on the Nike FuelBand
        \item Algorithms include FFT, Decision Trees and K Nearest Neighbor.
        \item Embedded C programming on Nike FuelBand.
        \item Worked with Python, C, Bash, Make and Git.
    \end{itemize}

    \textbf{Research Assistant}, \emph{NASA JPL, Pasadena, CA} \hfill \emph{Summer 2012}\\
    \vspace*{-4pt}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Researched and applied Machine Learning to estimate tree heights across North America.
        \item Algorithms include Decision Tree Learning, Random Forests and Linear Regression.
        \item Built and tested tools to analyze hundreds of gigabytes of atmospheric data.
        \item Worked with Python, C++, Bash, Make and Git.
    \end{itemize}

    \textbf{Software Engineer/Research Intern}, \emph{Tamarack Aerospace Group, Sandpoint, ID} \hfill \emph{Summer 2011}\\
    \vspace*{-4pt}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Researched load cycle counting algorithms for fatigue analysis calculations on small aircrafts.
        \item Responsible for implementing and testing algorithms efficiently and correctly.
        \item Data processing techniques involved Fast Fourier Transform and Band Pass Filters
        \item Worked with Fortran, PHP, Apache, Bash, and GNU Make.
    \end{itemize}

    \textbf {Software Engineer Intern}, \emph{NASA Goddard Space Flight Center} \hfill \emph{January 2010 - August 2010}\\
    \vspace*{-4pt}
    \begin{itemize} \itemsep -0pt  % reduce space between items
        \item Researched Laser Altimetry techniques for Space Flight and Autonomous Robots.
        \item Worked in a team to develop software for autonomous robot proof of concept in C++ and C\#.
        \item Implemented an A* like search algorithm for robot path planning to allow robots to autonomously navigate any environment.
        \item Specialized in Data Processing Techniques for Single Photon Detection Laser Altimeter
        \item Worked with SVN, Visual Studio, GCC, C, C++, and C\#.
    \end{itemize}

\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Education
\header{Education}

\begin{body}
    \vspace{14pt}

    % Western Washington University
    \textbf{B.S., Computer Science}{} \hfill \emph{September 2009 - December 2012}{} \\
    \textbf{Minors: Mathematics and Physics}\\
    \textbf{Major GPA: 3.7/4.0}\\
    \emph{Western Washington University}, Bellingham, WA{} \\
    %\medskip

    % Seattle Central Community College
    %\textbf{Associates of Science}{} \hfill \emph{September 2008 - August 2009} \\
    %\emph{Seattle Central Community College}, Seattle, WA{} \\
    %\medskip

    % Sandpoint High School
    %\textbf{High School Diploma} \hfill \emph{June 2007} \\
    %\emph{Sandpoint High School (SHS)}, Sandpoint, ID\\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Related Courses
\header{Relevant Courses}
\begin{body}
    \vspace{4pt}
    \begin{multicols}{2}
        \begin{itemize} \itemsep -0pt
            % Mathematics courses
            \item [] Single Variable Calculus I, II, \& III
            \item [] Multivariable Calculus I \& II
            \item [] Limits \& Infinite Series
            \item [] Ordinary Differential Equations
            \item [] Fourier Analysis \& Partial Differential Equations
            \item [] Linear Algebra I \& II
            \item [] Mathematical Modeling
            \item [] Probability \& Statistics
            \item [] Introduction to Complex Variables
            \item [] Linear \& Nonlinear Optimization

            % Computer Science courses
            \item [] Programming \& Linear Data Structures
            \item [] Discrete Structures \& Functional Programming
            \item [] Data Structures
            \item [] Analysis of Algorithms I \& II
            \item [] Computer Organization I \& II
            \item [] Database Systems
            \item [] Software Project Analysis \& Requirements
            \item [] Software Project Design
            \item [] Software Implementation
            \item [] Formal Languages \& Automata
            \item [] Unix Software Development
            \item [] Operating Systems
            \item [] Principles of Concurrent Programming
            \item [] Computer Networks
            \item [] Bioinformatics
            \item [] Compiler Theory and Design

            % Physics courses
            \item [] Computational Physics
            \item [] Quantum Mechanics
            \item [] Classical Mechanics
            \item [] Modern Physics
            \item [] Waves and Optics
            \item [] Electricity and Magnetism

            % Other Sciences
            \item [] General Chemistry I
            \item [] Molecular Biology
            \item [] Engineering Statics

        \end{itemize}
    \end{multicols}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Technical Skills

\header{Technical Skills}
\begin{body}
    \vspace{14pt}
    % Programming Languages
    \emph{\textbf{Programming Languages:}}{} Java, C++, Python, Ada, C, C\#, R, SQL, Scheme, NASM Assembly Language\\
    \medskip
    % Source Control
    \emph{\textbf{Unix Tools:}}{} Git, Bash, Vim, Lex, Yacc/Bison\\
    \medskip
    % Operating Systems
    \emph{\textbf{Operating Systems:}}{} Mac OS X, Linux, UNIX, Linux (Debian, Ubuntu, Gentoo)\\
    \medskip
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Awards and Honors
\header{Awards and Honors}

\begin{body}
    \vspace{14pt}


    % Yelp Hackathon
    \textbf{Most Useful Award}, Yelp Hackathon \hfill{} \emph{2013}\\
    \smallskip

    % Mathematical Modeling Competition
    \textbf{Honorable Mention}, Mathematical Modeling Contest \hfill{} \emph{2012}\\

\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Hobbies
\header{Hobbies}

\begin{body}
    \vspace{14pt}

    Programming, Electronics, reading, soccer, unicycling, swimming, skiing, and traveling
    % Yelp Hackathon
    %\textbf{Most Useful Award}, Yelp Hackathon
    %\smallskip

\end{body}

\end{document}
