\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{multicol}

% Various Document Settings
\leftmargin=0.15in
\oddsidemargin=0.15in
\textwidth=6.0in
\topmargin=-0.20in
\textheight=9.25in
\raggedright
\pagenumbering{arabic}
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

%% BEGIN DEFINITIONS %%

% New configurations for lists
\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}


\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

% Header
\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  		\lineover
	\end{changemargin}
}

% Contact Display Format
\newcommand{\contact}[4]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip 
			{#3}\\ \smallskip
			{#4}\smallskip
		\end{center}
	\end{changemargin}
}

% Document Margins
\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.20in}{-0.5in}
  }	
	{\end{changemargin}
}	

% School Display Format
%\newcommand{\school}[4]{
%	\textbf{#1} \hfill \emph{#2\\}
%	#3\\ 
%	#4\\
%}

%% BEGIN DOCUMENT %%

\begin{document}

% Contact Information
\contact{Travis W. Peters}{101 S. $43^{rd}$ St., Bellingham, WA 98229}{traviswp@gmail.com}{360.441.7304}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Objective
%\header{Objective}

%\begin{body}
%\vspace{14pt}
%Seeking a position in academic leadership or professional industry opportunities that utilizes my communication, analytical thinking and problem-solving skills to encourage, nurture and guide student creativity and learning.
%\end{body}

%\smallskip

% Professional summary
%\header{Professional Summary}

%\begin{body}
%\vspace{14pt}
%Professional student double majoring in Math \& Computer Science, working as Vice President for Business \& Operations of university student government, and leading a small technical team in part-time internship. Has particular expertise in problem solving, critical thinking, organization, individual and group goal-setting, facilitating collaboration and communicating in/with small and large groups. 
%\end{body}

%\smallskip

% Qualifications Summary
\header{Qualifications Summary}

\vspace{14pt}
\begin{body}
Motivated student with dual concentration in Mathematics \& Computer Science. Proven leadership capabilities serving as student representative in student
government, and managing other student managers in non-profit organization. Strong background and technical skills related to area of study demonstrated by
leading a team of interns in mobile application development, developing software extensions for corporate fraud management system, and teaching/tutoring
students as a Teaching Assistant for introductory Computer Science courses. 	

\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Education
\header{Education}

\begin{body}
	\vspace{14pt}
	
	% Dartmouth College
	\textbf{Ph.D., Computer Science}{} \hfill \emph{September 2013 - June 2018 (expected)}{} \\
	\emph{Dartmouth College}, Hanover, NH{} \\
	\medskip

	% Western Washington University
	\textbf{B.S., Double Major in Mathematics and Computer Science}{} \hfill \emph{September 2008 - December 2012}{} \\
	\emph{Western Washington University (WWU)}, Bellingham, WA{} \\
	%\medskip
	
	% University of Washington
	%\textbf{B.S., Mathematics} \hfill \emph{Winter 2009 - Fall 2009} \\
	%\emph{University of Washington}, Seattle, WA\\	
	%\medskip
	
	% Lower Columbia College
	%\textbf{Associate in Arts (Running Start)} \hfill \emph{June 2008} \\
	%\emph{Lower Columbia College (LCC)}, Longview, WA\\
	%\medskip
	
	% Kelso High School
	%\textbf{High School Diploma} \hfill \emph{June 2008} \\
	%\emph{Kelso High School (KHS)}, Kelso, WA\\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Experience
\header{Relevant Work Experience}

\begin{body}
	\vspace{14pt}

	\textbf{DevOps Contractor}, \emph{Attachmate, Bellingham, WA} \hfill \emph{January 2013 - August 2013}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Design and build a VM template management infrastructure using Opscode Chef and VMware's vCloud Director to maintain (patch \& update) a variety of systems (development to be done primarily in Ruby).
		\item Work with team members to define and build components for the Attachmate support website.
		\item Define and build reporting automation to improve analytics dashboard.
		\item Create Ruby, Bash, and Batch scripts to automate routine tasks. 
		\item Document processes, infrastructure/components, configurations and systems as needed. 
	\end{itemize}

	\textbf{Software Engineer Intern}, \emph{Attachmate, Bellingham, WA} \hfill \emph{August 2012 - December 2012}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Generalized the solution for the Sentinel Extensions for Luminet solution to support logging to various Security Information \& Event Management (SIEM) systems.
		\item Designed a customizable XML configuration file, wrote the related StAX parser, and developed various implementations of generic data structures to support the generic logging solution for Luminet. 
		\item Substantial focus on unit testing \& automated testing methods. 
		\item Co-authored and Delivered a presentation/demonstration of project results to the Luminet Product team.		
	\end{itemize}
	
	\textbf{Computer Science Teaching Assistant}, \emph{WWU, Bellingham, WA} \hfill \emph{September 2012 - Present}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Proctored two labs for Computer Science 140 (Programming Fundamentals in C++)
		\item Helped students understand fundamental concepts behind the C++ programming language, elementary data structures, basic building and compilation on UNIX systems, and simple sorting/searing algorithms.  
		\item Regularly held office hours \& graded laboratory assignments. 
	\end{itemize}
	
	\textbf{iOS Developer \& Intern Team Lead}, \emph{Emergency Reporting, Bellingham, WA} \hfill \emph{January 2012 - June 2012}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Developed requirements document and design for Emergency Reporting mobile application. 
		\item Led team of four interns to implement compatible mobile application on iOS and Android platforms. 
		\item Implemented features such as: secure communication across network and encryption/decryption of data (meets Department of Defense Standards), local and cloud database access and storage, and GPS related functionality for way-finding including integration with Google Maps.  
	\end{itemize}

	\textbf{Vice President for Business \& Operations}, \emph{Associated Students of WWU,} \hfill \emph{June 2011 - June 2012}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Charged with overseeing the internal operations of the Associated Students of Western Washington University (ASWWU) programs, services, and the facilities in which they operate.
		\item Directly managed six other student managers of departments with 1-20 employees. 
		\item Facilitated organizational budgeting process, assessment process as well as hiring process. 
		\item Specifically responsible for development of fiscal year 2012 operating \& non-operating budget (approximately \$3.1 million total). 
	\end{itemize}

	\textbf {Private Math Tutor}, \emph{Self-employed} \hfill \emph{September 2008 - Present}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Privately tutored more than 10 students in Mathematics while at Western Washington University.
		\item Demonstrated tutoring proficiency in algebra, geometry, pre-calculus, business calculus, single and multi-variable calculus, linear algebra, differential equations, and probability \& statistics. 
	\end{itemize}
	
	\textbf {Marketing \& Technical Associate}, \emph{Caso Inc., San Antonio TX} \hfill \emph{June 2010 - January 2011}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Collaborated with the marketing team to implement search engine optimization of company website.
		\item Advised a team of leaders from various departments to implement a trial of a new organizational management system intended for data storage of products, project information/status \& client records. 
	\end{itemize}

	\textbf {Teaching Assistant}, \emph{Family House Academy, Kelso, WA} \hfill \emph{Summer 2009}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item  Taught and tested students, ranging from 7-15, in Math, Reading, Writing, and Physical Education. 
		\item Designed lesson plans and evaluation metrics to gauge student progress. 
	\end{itemize}

\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Publications
\header{Selected Publications}

\begin{body}
	\vspace{14pt}
	Travis Peters, Chip Jackson \& Lucas Bourne. ``\textbf{Computing Along the Big Long River},'' \\
	\emph{UMAP Journal for Undergraduate Mathematics \& Research 33.3 Fall 2012 Edition - \\ 
	\hspace{5mm} The 2012 MCM / ICM Contest Edition}\\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Related Courses
\header{Relevant Courses}
\begin{body}
	\vspace{4pt}
	\begin{multicols}{2}
		\begin{itemize} \itemsep -0pt
			%mathematics courses
			\item [] Single Variable Calculus I, II, \& III
			\item [] Multivariable Calculus I \& II
			\item [] Limits \& Infinite Series
			\item [] Systems of Differential Equations
			\item [] Linear Algebra I \& II
			\item [] Introduction to Proofs via Number Theory
			\item [] Proofs in Elementary Analysis
			\item [] Introduction to Abstract Algebra
			\item [] Mathematical Modeling
			\item [] Probability \& Statistics
			\item [] Statistical Methods
			\item [] Introduction to Complex Variables
			\item [] Historical Perspectives of Mathematics
			
			%computer science courses
			\item [] Programming \& Linear Data Structures
			\item [] Discrete Structures \& Functional Programming
			\item [] Data Structures
			\item [] Analysis of Algorithms I \& II
			\item [] Computer Organization I \& II
			\item [] Database Systems
			\item [] Web Scripting
			\item [] Software Project Analysis \& Requirements
			\item [] Software Project Design
			\item [] Software Implementation
			\item [] Numerical Computation \& Analysis
			\item [] Object Oriented Programming in C++
			\item [] Formal Languages \& Automata
			\item [] Unix Software Development
			\item [] Operating Systems
			\item [] Principles of Concurrent Programming
			\item [] Computer Networks
			\item [] Cyber Defense Seminar
		\end{itemize}
	\end{multicols}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Technical Skills

\header{Technical Skills}
\begin{body}
	\vspace{14pt}
	% Programming Languages
	\emph{\textbf{Programming Languages:}}{} Ruby, Java, C++, Python, Ada, C, Matlab, Objective-C, PHP, Mathematica, HTML, CSS, SQL, Scheme, Prolog, Haskell, KPL, NASM Assembly Language\\
	\medskip
	% Source Control
	\emph{\textbf{Source Control:}}{} Git, Perforce\\
	\medskip
	% Operating Systems
	\emph{\textbf{Operating Systems:}}{} Mac OS X, Linux, UNIX, Windows\\
	\medskip
	% Industry Software/Systems
	\emph{\textbf{Industry Software/Systems:}}{} VMware's vCloud Director, Opscode Chef\\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Leadership
\header{Leadership Activities}

\begin{body}
	\vspace{14pt}
	\textbf{Lead Teacher \& RK Coordinator}, Redeemer Kids at Redeemer Church \hfill{} \emph{November 2011 - June 2013}\\
	\smallskip
	\textbf{Chair}, AS Management Council \& AS Facilities \& Services Council \hfill {} \emph{June 2011 - June 2012}\\
	\smallskip
	\textbf{Vice-Chair}, AS Board of Directors \& AS Budget Committee \hfill {} \emph{June 2011 - June 2012}\\
	\smallskip
	\textbf{Member}, Academic Honesty Board \hfill{} \emph{June 2011 - June 2012}\\
	\smallskip
	\textbf{Big Brother}, Big Brothers Big Sisters of Whatcom County \hfill{} \emph{September 2010 - September 2011}\\
\end{body}

\smallskip

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Awards and Honors
\header{Awards and Honors}

\begin{body}
	\vspace{14pt}
	
	% Dartmouth Fellowship
	\textbf{Dartmouth Fellowship}, Dartmouth College \hfill{} \emph{2013 - 2014}\\
	\smallskip
		
	% Oscar Edwin Olson Scholarship
	\textbf{Oscar Edwin Olson Scholarship}, Western Washington University \hfill{} \emph{2012}\\
	\smallskip
	
	% Outstanding Winner/Frank Giordano Award
	\textbf{Outstanding Winner, Frank Giordano Award}, Mathematical Contest in Modeling \hfill{} \emph{2012}\\
	\hspace{5mm}\textit{The Mathematical Contest in Modeling challenges students to clarify, analyze, and propose}\\
	\hspace{5mm}\textit{solutions to open-ended problems. The contest included over 3,600 teams from 17 countries}\\
	\hspace{5mm}\textit{around the world. Only 10 teams are selected as Outstanding Winners of the contest.}\\
	\smallskip
	
	% Kaiser Borsari Scholarship
	\textbf{Kaiser Borsari Scholarship}, Western Washington University \hfill{} \emph{2011 - 2012}\\
	\smallskip
	
	% Giusti Scholarship
	\textbf{Giusti Scholarship}, Western Washington University \hfill{} \emph{2011 - 2012}\\
	\smallskip
	
	% WWU Cross Country
	\textbf{4-year member of Junior Varsity Cross Country}, Western Washington University \hfill{} \emph{2008 - 2011}\\
	\smallskip
	
	% WWU Track & Field
	\textbf{4-year member of Varsity Track \& Field}, Western Washington University \hfill{} \emph{2008 - 2012}\\

\end{body}

\end{document}
